### 2016-11-16 paper/evaluation.tex
work in progress - fixes and updates on RQ1

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
Search API imposes the limit of 1,000 results regardless of the number
of matches from a search criteria.} Java projects with at least 100
stars. The number of stars indicates the interest and appreciation
from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml}), Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
the following values after updating the subject selection approach.}
From the 1,000 downloaded projects, we detected the build system of
801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
and considered 164 projects that we were able to compile (153 Maven
and 9 Ant projects).  We were unable to compile other subjects because
some are related to a particular platform (\eg, Gradle implied
Android), unsolved dependencies, or the build process is based on
user-defined tasks (\eg, we considered the name \emph{compile} on Ant
projects).

@@

\begin{itemize}
    \item \RQA
\end{itemize}

To evaluate the frequency of time-consuming regression tests, we
considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
that we were able to test. For each subject, we first compiled the
source files and later, we ran the tests and used regular expressions
to collect the elapsed time reported from the build system. To avoid
inflating the time cost from test execution, we ignored non-related
tasks (\eg, \emph{javadoc} generation). \Fix{elaborate: In case of
\emph{Maven} projects, we use \Jbc{How to show the following command?}
\Fix{mvn test -Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant}
projects, we used \Fix{ant test} and manually inspected the test
execution to ignore any non-related tasks, if any}.

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group.  Results indicate that a relatively
high number of projects from the sample set requires at least five
minutes to execute. The longest execution takes \Fix{x} to finish. It
is important to mention that Figure~\ref{fig:piechart-time} represents
a lower bound for elapsed time: some tests may finish early due to a
failure since the subjects were tested in a potentially unstable
revision.

>>>>

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
Search API imposes the limit of 1,000 results regardless of the number
of matches from a search criteria.} Java projects with at least 100
stars. The number of stars indicates the interest and appreciation
from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml}), Gradle
(\emph{*.gradle} file), and Ant (\emph{build.xml}).\Jbc{Remember to
update the following values after updating the subject selection
approach.} From the 1,000 downloaded projects, we detected the build
system of \Fix{801} subjects (composed by 216 Maven, \Fix{564} Gradle,
and 21 Ant projects) and considered \Fix{164} Maven projects that we
were able to compile and test.  We were unable to compile other
subjects because some of them are related to a particular platform
(\eg, Gradle implied Android), has unsolved dependencies (\eg, package
no longer available from the Maven public repository), or the build
process is based on user-defined tasks (\eg, Ant projects).

@@

\begin{itemize}
    \item \emph{\RQA}
\end{itemize}

To evaluate the frequency of time-consuming regression tests, we
considered the \Fix{X} Maven projects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.  To avoid inflating
the measured time, we first compile the sources files (see
Figure~\ref{fig:mvn-execution}, line 1) and later (see
Figure~\ref{fig:mvn-execution}, line 2), we ran the tests ignoring
non-related tasks (\eg, \emph{javadoc} generation). In addition, when
we run a subject's test suite, we operate Maven in offline mode to
limit the network access, avoiding any unnecessary package update as
all required \emph{jars} are available locally. After the test
execution, we use a simple regular expression over the builder output
to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Compiling and testing a Maven
    subject: line 1 compiles all subject's source artifacts and make
    them available in a local repository (\ie, directory \emph{.m2} in
    the user's home directory); line 2 runs the tests in offline mode
    ignoring javadoc generation.}
\end{figure}

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group.  Results indicate that a relatively
high number of projects from the sample set (\ie, 17\%) requires at
least five minutes to execute. The longest execution takes \Fix{x} to
finish. It is important to mention that Figure~\ref{fig:piechart-time}
represents a lower bound for elapsed time: some tests may finish early
due to a failure since the subjects were tested in a potentially
unstable revision.
